Verifying Demonstrations

### 2018-05-23 paper/LocationProofs.tex
Edits related work

Some Location-Based Services (\emph{LBS}) only grant access to resources to users located at a particular location,  thus raising the issue of verifying the position claimed by a particular user. 
In most current schemes, the location of a user/device is determined by the device itself (\eg through GPS) and forwarded to the LBS provider. 
One of the main drawback of this approach is that a user can cheat by having his device transmitting a false location. 
Therefore, it is possible for a user to be inappropriately granted access to a particular resource while being thousands of kilometers away.

To counter this threat, a LBS should ask the requesting device to formally prove that it really is at the claimed location. This notion can be formalized through the concept of \emph{location proof}. 
In a nutshell, a location proof is a digital certificate attesting that someone was at a particular location at a specific moment in time. A location proof architecture is a system by which users can obtain location proofs from neighboring witnesses (\eg trusted access points or other users) that can later be shown to verifiers who can check the validity of a particular proof. 
Most of the existing approaches to location proofs require the prover and the witnesses to disclose their identities, thus raising many privacy issues such as the possibility of tracing the movements of users of the location proof architecture.
%Seb: to do add the corresponding reference
However, some location proofs systems such as PROPS exists that provides strong privacy guarantees along with the possibility of verifying the claim of the location. 
\PRIVO share some similarities with PROPS although their objective is quite different as we aim at verifying a global property of the population (\ie crowd estimation) in contrast to checking the location claim made a user, which is an individual property.

>>>>

Some \ac{LBS} only grant access to resources to users located at a particular 
location,  thus raising the issue of verifying the position claimed by a 
particular user. In most current schemes, the location of a user/device is 
determined by the device itself (\eg through GPS) and forwarded to the \ac{LBS} 
provider. One of the main drawback of this approach is that a user can cheat by 
having his device transmitting a false location. Therefore, it is possible for a 
user to be inappropriately granted access to a particular resource while being 
thousands of kilometers away.

To counter this threat, \iac{LBS} should ask the requesting device to formally 
prove that it really is at the claimed location. This notion can be formalized 
through the concept of \emph{location proof}. In a nutshell, a location proof is 
a digital certificate attesting that someone was at a particular location at a 
specific moment in time. A location proof architecture is a system by which 
users can obtain location proofs from neighboring witnesses (\eg trusted access 
points or other users) that can later be shown to verifiers who can check the 
validity of a particular proof. Most of the existing approaches to location 
proofs require the prover and the witnesses to disclose their identities, thus 
raising many privacy issues such as the possibility of tracing the movements of 
users of the location proof architecture.
\seb{to do add the corresponding reference}
However, some location proofs systems, such as \ac{PROPS}, exists that provides 
strong privacy guarantees along with the possibility of verifying the claim of 
the location. \PRIVO share some similarities with \ac{PROPS}, although their 
objective is quite different as we aim at verifying a global property of the 
population (\ie crowd estimation) in contrast to checking the location claim 
made by a user, which is an individual property.

### 2018-05-23 paper/RelatedWork.tex
Edits related work

The seemingly most commonly used method for counting crowds at protests is \emph{Jacob's method}~\cite[c.f.][]{%
  2016DemonstrationsInSeoul,%
  BBCHowToCountProtestNumbers,%
  HowWillWeKnowTrumpInauguralCrowdSize,%
  TheXManMarch,%
  TheCrowdNumbersGame,%
}.
It is a manual method devised in the 1960s relying on aerial photos of the event.
The verifier divides the protest venue into regions and then estimates the density of the crowd in the different regions and finally sums them up to get an estimate of the global count.
Clearly this method is prone to errors as it is based on estimates.
It provides universal verifiability (\cref{UniversalVerif}) since anyone can redo the counting using the same photos.
However, it is difficult to achieve individual verifiability (\cref{IndividualVerif}) using this method since it is hard to verify that oneself is indeed in any of the photos\footnote{It is of course possible with very detailed photos, but not currently realistic to do with aerial photos.}.
We can argue that it also achieves eligibility (\cref{EligibilityVerif}) if all the photos are taken at the same point in time with no overlap, since then no one can be counted twice.
Unfortunately, we can only get the peak participation with this method.
When it comes to spatial and temporal eligibility, we have to rely on pictures (\eg by determining from the photos themselves when and where the they were taken).
However, this is prone to cheating and the best we can do is to employ forensic methods to try to detect any modifications or other attempts at fraud.
\seb{maybe we should also give information about the privacy level reached by 
  this different method}

@@

In the computer vision community, there is a body of work on estimating the number of persons in a picture (\eg the work of 
\citet{NNCrowdCounting}).
This class of methods requires photos or video surveillance of the protest location during the entire protest and are thus highly privacy-invasive.
They generally based on machine learning, and thus also require a training dataset to work.
In the work by \citet{NNCrowdCounting}, they actually train and evaluate their algorithm on different scenes, which might make this method easier to use for protesting.
Universal verifiability (\cref{UniversalVerif}) can be provided with this method, since someone can always recount the participants using the recorded video material.
Some degree of individual verifiability could also be provided (\cref{IndividualVerif}), if Alice can recognize her own face in the video, but this might still be difficult. 
Note also that while automatic face recognition can help verifiability, it has a high impact on privacy.
Also, it is difficult (if not impossible) to not count people twice, thus we cannot argue for eligibility (\cref{EligibilityVerif}).
In theory, this class of methods will provide an upper bound, whereas our method outputs a lower bound.
However, it is still difficult to capture the entire location on surveillance video, which diminishes the argument for an upper bound.
The spatial and temporal verifiability properties are reduced to those of the video, which should be similar as in our discussion about the verifiability of photos (\ie, using forensic methods).

@@

During the protests in Seoul~\cite{2016DemonstrationsInSeoul}, one physical analytics company has tried to estimate the number of participants using their technology.
They scanned for MAC addresses emitted from the Wi-Fi of participants' smartphones.
However, this method required many assumptions:
\blockcquote{2016DemonstrationsInSeoul}{%
  The company presumed that about half of smartphone users usually leave their Wi-Fi feature on and the other half switch it off, based on a separate survey on smartphone usage. 
It also assumed that about 20\% of the smartphone signals were repetition from the same device.
}
This method cannot provide any verifiability, as we must trust the company in doing the measurements correctly and to be honest about when and where they did them.
As MAC address randomization get wider adoption, this will be even more difficult, although some tracking of smartphones could still be possible~\cite{WhyMACRandomizationIsNotEnough}.

A better proposal would be to use \emph{IMSI catchers} (or the real cell towers of the mobile network) to count unique phones at a location.
However, there are several problems with this approach.
First, it will be difficult to register only the participants' phones and many bystanders will also be counted.
It is also difficult to differentiate between the protesters and the counter-protesters.
Second, since the phone has a unique identifier, participants might be uncomfortable to be registered in association with the event and might thus turn the device off, even though, at least with 5G, the IMSI will not be
transmitted in plaintext anymore. %need to cite?
Finally, there will be limited verifiability, as the data recorder must be trusted to record all data in the relation to the protest.

\Citet{WifiCrowdCounting} also relies of Wi-Fi, but they instead use the Wi-Fi signal as a sonar to detect people.
Howeve,r this method is designed for indoor use and does not scale to more than a crowd of 20 persons, which makes it unfit to use in protest.
In addition, this type of data does not provide verifiability.

@@

One of the most closely related work to our scheme is \citet{CrowdCount}, which is a web service that lets Alice create an event such that anyone can submit his location to register that he is in Alice's event.
This method has the benefit of counting everyone who has declared his presence, not just the count at the snapshot of the photos.
However, there is no verification as the service must be trusted to behave honestly, but even then, nothing prevents Bob from submitting twice (violating eligibility, \cref{EligibilityVerif}).
Another downside is that the service also requires an Internet connection during the event to register as a participant.
This makes it prone to some form of denial-of-service attack.
For instance, if Alice has organized a protest against Eve's regime, who shuts down the cellular network or Internet backbone as a means to censor the protest.

Another related approach based on devices is UrbanCount~\cite{UrbanCount}, which uses epidemic spreading of crowd-size estimates by device-to-device communication to count crowds in dense urban environments with highnode mobility and churn. There is, however, no consideration of a potentially adverserial setting and thus no verification or checks on eligibility. DiVote~\cite{DiVote}, a prior work by the same authors for polling in dense areas, avoids double counting but again only work for
honest participants.

>>>>

The seemingly most commonly used method for counting crowds at protests is 
\emph{Jacobs's method}, \cf~\cite{%
  2016DemonstrationsInSeoul,%
  BBCHowToCountProtestNumbers,%
  HowWillWeKnowTrumpInauguralCrowdSize,%
  TheXManMarch,%
  TheCrowdNumbersGame,%
}.
It is a manual method devised in the 1960s relying on aerial photos of the event.
The verifier divides the protest venue into regions and then estimates the density of the crowd in the different regions and finally sums them up to get an estimate of the global count.
Clearly this method is prone to errors as it is based on estimates.
It provides universal verifiability (\cref{UniversalVerif}) since anyone can redo the counting using the same photos.
However, it is difficult to achieve individual verifiability (\cref{IndividualVerif}) using this method since it is hard to verify that oneself is indeed in any of the photos\footnote{It is of course possible with very detailed photos, but not currently realistic to do with aerial photos.}.
We can argue that it also achieves eligibility (\cref{EligibilityVerif}) if all the photos are taken at the same point in time with no overlap, since then no one can be counted twice.
Unfortunately, we can only get the peak participation with this method.
When it comes to spatial and temporal eligibility, we have to rely on pictures (\eg by determining from the photos themselves when and where the they were taken).
However, this is prone to cheating and the best we can do is to employ forensic methods to try to detect any modifications or other attempts at fraud.
\seb{maybe we should also give information about the privacy level reached by 
  this different method}

@@

In the computer vision community, there is a body of work on estimating the number of persons in a picture (\eg the work of 
\citet{NNCrowdCounting}).
This class of methods requires photos or video surveillance of the protest location during the entire protest and are thus highly privacy-invasive.
They are generally based on machine learning, and thus also require a training 
dataset to work.
In the work by \citet{NNCrowdCounting}, they actually train and evaluate their algorithm on different scenes, which might make this method easier to use for protesting.
Universal verifiability (\cref{UniversalVerif}) can be provided with this method, since someone can always recount the participants using the recorded video material.
Some degree of individual verifiability could also be provided (\cref{IndividualVerif}), if Alice can recognize her own face in the video, but this might still be difficult. 
Note also that while automatic face recognition can help verifiability, it has a high impact on privacy.
Also, it is difficult (if not impossible) to not count people twice, thus we cannot argue for eligibility (\cref{EligibilityVerif}).
In theory, this class of methods will provide an upper bound, whereas our method outputs a lower bound.
However, it is still difficult to capture the entire location on surveillance 
video, which diminishes the argument for an upper bound in practice.
The spatial and temporal verifiability properties are reduced to those of the video, which should be similar as in our discussion about the verifiability of photos (\ie, using forensic methods).

@@

During the protests in Seoul~\cite{2016DemonstrationsInSeoul}, one physical 
analytics company tried to estimate the number of participants using their 
technology.
They scanned for MAC addresses emitted from the Wi-Fi of participants' smartphones.
However, this method required many assumptions:
\blockcquote{2016DemonstrationsInSeoul}{%
  The company presumed that about half of smartphone users usually leave their Wi-Fi feature on and the other half switch it off, based on a separate survey on smartphone usage. 
It also assumed that about 20\% of the smartphone signals were repetition from the same device.
}
This method cannot provide any verifiability, as we must trust the company in doing the measurements correctly and to be honest about when and where they did them.
As MAC address randomization get wider adoption, this will be even more difficult, although some tracking of smartphones could still be possible~\cite{WhyMACRandomizationIsNotEnough}.

A better proposal would be to use \emph{IMSI catchers} (or the real cell towers of the mobile network) to count unique phones at a location.
However, there are several problems with this approach.
First, it will be difficult to register only the participants' phones, as many 
bystanders will also be counted.
It is also difficult to differentiate between the protesters and the counter-protesters.
Second, since the phone has a unique identifier, participants might be uncomfortable to be registered in association with the event and might thus turn the device off, even though, at least with 5G, the IMSI will not be
transmitted in plaintext anymore. %need to cite?
Finally, there will be limited verifiability, as the data recorder must be trusted to record all data in the relation to the protest.

\daniel{I think we can cut this paragraph as it is not directly relevant}
\Citet{WifiCrowdCounting} also relies of Wi-Fi, but they instead use the Wi-Fi signal as a sonar to detect people.
However this method is designed for indoor use and does not scale to more than a 
crowd of 20 persons, which makes it unfit to use in protest.
In addition, this type of data does not provide verifiability.

@@

One of the most closely related work to our scheme is \citet{CrowdCount}, which is a web service that lets Alice create an event such that anyone can submit his location to register that he is in Alice's event.
This method has the benefit of counting everyone who has declared his presence, not just the count at the snapshot of the photos.
However, there is no verification as the service must be trusted to behave honestly, but even then, nothing prevents Bob from submitting twice (violating eligibility, \cref{EligibilityVerif}).
Another downside is that the service also requires an Internet connection during the event to register as a participant.
This makes it prone to some form of denial-of-service attack.
For instance, if Alice has organized a protest against Grace's regime, who shuts 
down the cellular network or Internet backbone as a means to censor the protest.

Another related approach based on devices is UrbanCount~\cite{UrbanCount}, which 
uses epidemic spreading of crowd-size estimates by device-to-device 
communication to count crowds in dense urban environments with high 
node-mobility and churn. There is, however, no consideration of a potentially 
adverserial setting and thus no verification or checks on eligibility. 
DiVote~\cite{DiVote}, a prior work by the same authors for polling in dense 
areas, avoids double counting, but again, only work for honest participants.
